Intro to Data

### 2018-08-31 DATA606/Intro to Data.Rmd
More work on Intro to Data assignment
Renamed 1_70.png to 1_70_1.png b/c there are
more than one 1_70 pngs

@@

![ ](https://github.com/mikeasilva/CUNY-SPS/raw/master/DATA606/intro_to_data_1_70.png)

@@

@@

@@

ii. The paragraph below describes the set up for such approach, if we were to do it withut using statistical software. Fill in the blanks with a number or phrase, whichever is appropriate.

We write alive on cards representing patients who were alive at the end of the study, and dead on cards representing patients who were not. Then, we shuffle these cards and split them into two groups: one group of size representing treatment, and another group of size representing control. We calculate the difference between the proportion of dead cards in the treatment and control groups (treatment - control) and record this value. We repeat this 100 times to build a distribution centered at . Lastly, we calculate the fraction of simulations where the simulated differences in proportions are . If this fraction is low, we conclude that it is unlikely to have observed such an outcome by chance and that the null hypothesis should be rejected in favor of the alternative.

@@

>>>>

## Description

The following is the graded problems for the Intro to Data chapter of Open Intro to Statistics.  My answers to the questions are **bolded.**  The headers correspond to a question.

@@

![ ](https://github.com/mikeasilva/CUNY-SPS/raw/master/DATA606/intro_to_data_1_70_1.png)

@@

**It suggests that the survival time of those receiving the treatment is larger than the control group.**

@@

**Roughly 88% of the control group and 65% of the treatment group died when the box plot was made.  Eventually 100% of both groups died.**

@@

**That the treatment is effective at increasing the duration of life.**

ii. The paragraph below describes the set up for such approach, if we were to do it without using statistical software. Fill in the blanks with a number or phrase, whichever is appropriate.

We write alive on **28** cards representing patients who were alive at the end of the study, and dead on **75** cards representing patients who were not. Then, we shuffle these cards and split them into two groups: one group of size **69** representing treatment, and another group of size **34** representing control. We calculate the difference between the proportion of dead cards in the treatment and control groups (treatment - control) and record this value. We repeat this 100 times to build a distribution centered at **zero**. Lastly, we calculate the fraction of simulations where the simulated differences in proportions are **less than zero**. If this fraction is low, we conclude that it is unlikely to have observed such an outcome by chance and that the null hypothesis should be rejected in favor of the alternative.

@@

![ ](https://github.com/mikeasilva/CUNY-SPS/raw/master/DATA606/intro_to_data_1_70_2.png)
